Supporting Information

### 2016-09-09 portfolio/text/supp.Rnw
Develop supplement text

<<get-values, cache=FALSE>>=
load("../data-generated/output-values.rda")
@

@@

\section{Data filtering}

<<nothing, eval=FALSE>>=
permit_rev = group_by(cfecnew, p_holder, year, p_fshy) %>%
  summarize(permit.rev = sum(g_earn)) %>%
  as_data_frame() %>%
  group_by(p_holder, year) %>%
  mutate(tot.rev = sum(permit.rev))
permit_rev$permit.rev = permit_rev$permit.rev/permit_rev$tot.rev # fraction of total
permit_rev = permit_rev[permit_rev$permit.rev < 0.1,]

# Delete these minimal earnings
cfecnew = cfecnew[-which(paste(cfecnew$p_holder, cfecnew$year, cfecnew$p_fshy) %in%
  paste(permit_rev$p_holder, permit_rev$year, permit_rev$p_fshy)), ]

cfecnew <- filter(cfecnew, p_spec != "Freshwater") # only 1400 rows
@

Rows of data initial: \Sexpr{round(ndat$initial/1e6,2)} million

Rows of data annual: \Sexpr{ndat$annual}

Rows of data diff: \Sexpr{ndat$annual_diff}

% \Sexpr{ndat$rev_b4_10perc/1e9}
% \Sexpr{round(ndat$rev_after_10perc/1e9,2)}

\Sexpr{ndat$before_10_perc}

Rows of data after 10,000 cull: \Sexpr{ndat$large_only}

10,000 cull: rev:
\Sexpr{round(1-ndat$rev_large_only/ndat$rev_b4_large_only,2)*100}

\Sexpr{round(ndat$rev_large_only/1e9,2)}

\section{Assigning strategies}

\Sexpr{nstrat$enough_pholders}

\Sexpr{round(ndat$rev_enough_pholders/1e9,2)}

\Sexpr{nstrat$no_river_exp}

\Sexpr{round(ndat$rev_no_river_exp/1e9,2)}

Number of strategies: \Sexpr{nstr}

Rows of data before no singles: \Sexpr{ndat$before_nosingles}

% \Sexpr{ndat$b4_no_na_strat}
%
% \Sexpr{ndat$rev_b4_no_na_strat}
%
% \Sexpr{ndat$after_no_na_strat}

lost \% rev no strat:
\Sexpr{round(ndat$rev_after_no_na_strat/ndat$rev_b4_no_na_strat,2)*100}

lost rows no strat:
\Sexpr{round(ndat$after_no_na_strat/ndat$b4_no_na_strat,2)*100}

% \Sexpr{ndat$rev_after_no_na_strat}
%
% \Sexpr{ndat$rev_final}

Rows of data: \Sexpr{ndat$final}

Number of permit holders: \Sexpr{npholders}

Range of years: \Sexpr{range_yrs}

Number of strategy-years: \Sexpr{nstr_yrs}

@@

@@

\begin{table}[h!]
  \centering
  \caption{Labels and descriptions of fishing strategies. In many cases,
a particular strategy represents a group of similar permits across areas
or vessel sizes. These strategies all had at least 100
permit holders.}
  \label{tab:strategies}
  \begin{tabular}{ll}
  \toprule
\input{../figs/strategy-table.tex}
  \end{tabular}
\end{table}

>>>>

<<get-values, cache=FALSE, echo=FALSE>>=
load("../data-generated/output-values.rda")
n_grouped_permits <- readRDS("../data-generated/n_grouped_permits.rds")
@

@@

\section{Filtering data and grouping permits into strategies}

We filtered the data in a number of ways before fitting our model. 
We began with \Sexpr{round(ndat$initial/1e6,2)} million rows of data.
We removed revenue from permit-year combinations 
that made up less than 10\% of annual revenue
for a given permit holder. 
We removed permit holders whose median revenue
was less than \$10,000 USD (adjusted to 2009 values)
to focus on individuals actively engaged 
in commercial fishing.
This reduced the total revenue from \Sexpr{round(ndat$rev_b4_large_only/1e9,0)}
billion 2009 USD
to \Sexpr{round(ndat$rev_large_only/1e9,0)} billion 2009 USD.

To limit the number of permits 
and permit strategies 
and focus on the main fisheries, 
we removed all permits with less than 50 unique permit holders 
across all years. 
We also removed permits for freshwater species and
for experimental fisheries.
A list of all CFEC permit codes and descriptions is available at:
\url{https://www.cfec.state.ak.us/misc/FshyDesC.htm}

We then proceeded to combine similar permits in the following steps. 
We combined a number of permits that were the same except for vessel size.
We combined permits for 
otter troll, 
longline finfish,
pot gear.
king crab, 
and
shrimp.
We grouped a number of permits that were targeting a single species 
and differed only in region fished.
For example, someone fishing herring roe in the Kodiak (G34K)
and someone fishing herring roe in Alaska Peninsula (G34M) 
were both considered to have a herring roe permit strategy.
We combined permits across each of 
dungeness crab, 
herring roe purse seining,
herring roe gillnet,
herring hand picked,
herring pound fishing,
sea cucumber,
sea urchin,
tanner crabs

Combining salmon permits was more difficult because 
the species composition varies widely based on geography. 
We grouped salmon permits within gear type-region 
combinations that shared similar species composition.
For the drift gillnet (S03) permits, 
we combined permits from 
Cook Inlet, Bristol Bay, and Alaska Peninsula because sockeye
represents greater than 90\% of species revenue.
For the purse seine permits (S01),
there was a wide variety in species revenue by
area ($\sim$ 85\% pink in Prince William Sound to
85\% sockeye on the Alaskan Peninsula). 
Of the five permits, only two had similar species compositions, 
so we grouped Kodiak and Cook Inlet.
For the set gillnet salmon permits (S04), 
there was some variety but also clear sockeye specialists. 
We grouped permits that had greater than 80\% sockeye revenue.
This combined permits across 
Prince William Sound, 
Cook Inlet,
Kodiak,
Alaska Peninsula,
and Bristol Bay.
We grouped permits from Norton Sound
and Kuskokwim because of similar species compositions.
The remaining salmon permits were relatively unique 
and were left ungrouped.

After this process of combining permits, 
we were left with \Sexpr{n_grouped_permits}
unique fishing strategies (Table~\ref{tab:strategies}),
which we aggregated
within each person-year combination.
For example, if someone fished halibut 
and sablefish in the same year 
their strategy for that year would be ``halibut-sablefish''.
We removed people who switched strategies from one year to the next
since we were working with changes in revenue from year to year
and so needed consistent strategies across any pair of years
for a permit holder.
We removed strategies with less than 100 unique permit holders
across all years to focus on the major strategies
leaving us with a total of \Sexpr{nstr} strategies.
Finally, we removed all person-year combinations without 
revenue recorded in the following year 
in order to calculate percent change in revenue
from year to year.
This reduced the rows (person-year combinations)
in the final dataset from \Sexpr{ndat$annual} to
\Sexpr{ndat$annual_diff}.

% Rows of data: \Sexpr{ndat$final}
% Number of permit holders: \Sexpr{npholders}
% Range of years: \Sexpr{range_yrs}
% Number of strategy-years: \Sexpr{nstr_yrs}
% \Sexpr{nstrat$enough_pholders}
% \Sexpr{round(ndat$rev_enough_pholders/1e9,2)}
% lost \% rev no strat:
% \Sexpr{round(ndat$rev_after_no_na_strat/ndat$rev_b4_no_na_strat,2)*100}
% lost rows no strat:
% \Sexpr{round(ndat$after_no_na_strat/ndat$b4_no_na_strat,2)*100}

@@

Describe predictors

We adjusted for inflation by setting all revenues 2009 USD.

We calculated Simpson's diversity index weighted by revenue
as: 1/sum((x/sum(x)) squared)

@@

\begin{table}[h!]
  \centering
  \caption{Labels and descriptions of fishing strategies. In many cases,
a particular strategy represents a group of similar permits across areas
or vessel sizes.}
  \label{tab:strategies}
  \begin{tabular}{ll}
  \toprule
\input{../figs/strategy-table.tex}
  \end{tabular}
\end{table}
